### 2015-11-20 Thesis Draft Tianpei Chen/Thesis Draft/C-GA.tex
update PL

Figure (\ref{}) shows the flow chart of the proposed hybrid GA. In the beginning, the initial solution of CSVPD is fed to GA, a initial population of solutions are generated based on this initial solution, then in each iteration, each candidate solution is evaluated and selected by fitness function. The elites are selected as parents which can generate offspring. The offsprings are generated by recombining a pair of parents, this process is called crossover. Then mutation operates to offsprings with a given possibility. OPIC is integrated in GA as an operator that can accelerate the process that GA approximate to optimal solution. The populations is finally reconstructed by the parents and their offsprings. The best solution is chosen when the stopping criteria satisfied.

\subsection{Initialization}
\subsection{Selection}
\subsection{Mutation}
\subsection{OPIC} 
\subsection{Stopping Criteria}

>>>>

Figure (\ref{}) shows the flow chart of the proposed hybrid GA. In the beginning, the initial solution of CSVPD is fed to GA, a initial population of solutions are generated based on this initial solution, then in each iteration, each candidate solution is evaluated and selected by the fitness function. The elites are selected as parents which can generate offspring. The offsprings are generated by recombining a pair of parents, this process is called crossover. Then mutation operates to offsprings with a given possibility. OPIC is integrated in GA as an operator that can accelerate the process that GA approximate to optimal solution. The populations is finally reconstructed by the parents and their offsprings. The best solution is chosen based on the fitness function when the stopping criteria satisfied.

\subsection{Initialization}
Let $\mathbb{P}_{i}$ denotes the $i$th generation set consists of $|\mathbb{P}|$ symbol vectors, which is fixed in different generations. The estimated symbol vector from SVPD serves as the generation seed for the initial generation. The initial generation is generated by flipping a fix number of symbols to the nearest point in the symbol constellation alphabet randomly.

Let $\mathcal{F}$ denotes the number of symbols to be flipped. By flipping, a "$\mathcal{F}-coordinate-away$" neighbourhood symbol vector is generated, where "$\mathcal{F}-coordinate-away$" denotes the objective symbol vector has $\mathcal{F}$ coordinates different from the original symbol vector.

We now use a binary sequence generated by SVPD to illustrate how the flipping process works, let $b_{SVPD}\in \mathbb{B}^{N_{t}}, \mathbb{B}=[+1, -1], N_{t}=8$ denotes the the binary sequence generated by SVPD, 
\begin{equation}
b_{SVPD}=[1, -1, -1, 1, -1, 1, 1, -1],
\end{equation}  
$\mathcal{F}=1$, means there is one symbol difference between the original symbol vector and the objective symbol vector after flipping. Let $b_{1}, b_{2}, \ldots b_{|\mathbb{P}|-1}$ denotes the individuals in the initial generation which are generated by perturbing seed vector $b_{SVPD}$. Fig.\ref{random flipping} shows how this random flipping scheme works.
\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\include{randomFlipping.tex_pdf}
\caption{Random Flipping with $\mathcal{F}=1$}
\label{random fipping}
\end{figure}
The initial generation is $\mathbb{P}=[b_{SVPD}, b_{1}, b_{2}, \ldots b_{|\mathbb{P}|-1}$.
\subsection{Selection}
The individuals in each generation are evaluated by the fitness function. In LS-MIMO detection problem. Euclidean distance is used as the fitness function, given by 
\begin{equation}
f(\mathbf{s_{i}})=||\mathbf{y}-\mathbf{H}\mathbf{s}_{i}||^{2}, 
\label{fitness function}
\end{equation}
where $\mathbf{s}_{i}$ denotes the $i$th individual symbol vector in the generation, the individual with the smallest fitness function value is the fittest candidate (elite) in the generation.

In each generation, the individuals with small $f(\mathbf{s}_{i})$ are chosen as the parents to generate offsprings, the offsprings are generated by recombining the parent symbol vectors, this process is recombination or crossover. In crossover process, crossover point is randomly chosen in parent symbol vectors and the subpart of a pair of parent symbol vectors up to that crossover point are interchanged. A simple cased of this process is shown in Fig.\ref{crossover}.
\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\include{crossover.tex_pdf}
\caption{Crossover operation to a pair of parent binary sequence}
\label{crossover}
\end{figure}
\subsection{Mutation}
The GA in operates in a sub searching space, which is initially, determined by the $\mathcal{F}$ neighbourhood of the seed symbol vector. The major difficulties in the revolution process in the convergence to the local minima of the sub searching space. Mutation is a strategy that helps GA to escape from local minima. Mutations operates by randomly perturbation of a small number of coordinates in offspring symbol vectors with a small possibility defined by the users. Fig.\ref{mutation} shows how mutation works. 
\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\include{mutation.tex_pdf}
\caption{Mutation operation to one bit in binary sequence}
\label{mutaion}
\end{figure}
\subsection{OPIC} 
\subsection{Stopping Criteria}
